A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-12 application_to_path_tracing.tex
Petites corrections suite à la relecture de Michel

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$. $L_e$ is the emitted radiance that is not zero only on light sources. $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. $N_x$ is the surface normal at point $x$. The $f_r$ function is called the \myem{bidirectional reflectance function} (BRDF) and express the exchange of radiance between the incoming direction $\Phi$ and the output direction $\Theta$. Intuitively it represents the material properties of the surface at point $x$. A mirror does not reflect light the same manners a wall do and the BRDF describes that kind of behavior.

@@

This strategy of choosing an adapted pdf is called \myem{importance sampling} and is over-used in global illumination to improve the convergence of the algorithms.

The algorithm to compute $L$ is as follow: first we sample a random direction $\Phi$ based on the pdf $p$. Then we apply the estimator that call $L$ recursively to compute $L_r$. Finally we return the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reach.

This computation is done multiple time for each pixel (at different positions over the pixel). We average the results and get an estimation of the mean radiance passing through the pixel in direction of the camera's origin.

@@

The key idea behind our method is that light travels in the void of the scene. As stated in the introduction, a curvilinear skeleton of the void gives us enough informations to compute some importance directions where light comes from. Given these directions we can construct a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$

@@

\begin{equation*}
f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi)
\end{equation*}

It is a product of three functions that can be efficiently sample individually but that are hard to sample when they are combined. The most common strategy used to sample $\Omega_x$ is to use the BRDF (combined with the cosine) because we know it: it is given as an input of the algorithm, for exemple with textures.

$L$ is rarelly used because its evaluation cannot be done in constant time. Remember that it represents the distribution of light in the scene. It takes high values when $\Phi$ carries a lot of energy. Our method gives a way to sample according to $L$.

@@

The skeleton of the void is computed with our algorithm \ref{sec::skeletonization} and is converted to a graph (the nodes are 3D positions and the edges represents the topology of the scene), given as an input of our path tracing. We then compute a set of points called \myem{importance points}. These points will be used to sample $\Omega_x$ in the path tracing algorithm. For each node of the skeleton $n$, one importance point $imp_n$ is computed.

Let $L$ be a light of the scene ($L \in S_L$) and $n_L$ the shortest visible node by $L$. We first compute a tree of shortest paths along the skeleton with $n_L$ as root. We use the Dijkstra algorithm with a distance based on visibility from $n_L$: We put $d(n, m) = 1$ if $m$ is visible from $n_L$ and $d(n, m) = 10$ if not. It results that the paths that are enlighted by $L$ will have a shorter distance and will guide us to the light faster than the dark ones.

@@

\clearpage
\subsection{Results and discussion}

We present some results of our algorithm applied to four scenes. the first row shows our result and the second row shows a standard path tracing with the same input parameters. On each picture a MSE (mean square error) value with a reference image is shown.

@@

We presented an application of our skeletonization algorithm for global illumination. Our strategy works well, it reduces noise by taking into account the distribution of energy in the scene. One of the problem is that we take into account only one importance direction for sampling, totally ignoring the BRDF and the cosine factor. A solution called Multiple Importance Sampling will allow us to combine different strategies into one.

>>>>

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$. $L_e$ is the emitted radiance that is not zero only on light sources. $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. $N_x$ is the surface normal at point $x$. The $f_r$ function is called the \myem{bidirectional reflectance function} (BRDF) and expresses the exchange of radiance between the incoming direction $\Phi$ and the output direction $\Theta$. Intuitively it represents the material properties of the surface at point $x$. A mirror does not reflect light in the same manner as a wall does and the BRDF describes that kind of behavior.

@@

This strategy of choosing an adapted pdf is called \myem{importance sampling} and is used in global illumination to improve the convergence speed of the algorithms.

The algorithm to compute $L$ is as follow: first we sample a random direction $\Phi$ based on the pdf $p$. Then we apply the estimator that calls $L$ recursively to compute $L_r$. Finally we return the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reached.

This computation is done multiple times for each pixel (at different positions over the pixel). We average the results and get an estimation of the mean radiance passing through the pixel in direction of the camera's origin.

@@

The key idea behind our method is that light travels in the void of the scene. As stated in the introduction, a curvilinear skeleton of the void gives us enough information to compute some importance directions where light comes from. Given these directions we can construct a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$.

@@

\begin{equation*}
f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi).
\end{equation*}

It is a product of three functions that can be efficiently sampled individually but that are hard to sample when they are combined. The most common strategy used to sample $\Omega_x$ is to use the BRDF (combined with the cosine) because we know it: it is given as an input of the algorithm, for exemple with textures.

The term $L$ is rarely used because its evaluation cannot be done in constant time. Remember that it represents the distribution of light in the scene. It takes high values when $\Phi$ carries a lot of energy. Our method gives a way to sample according to $L$.

@@

The skeleton of the void is computed with our algorithm (section \ref{sec::skeletonization}) and is converted to a graph (the nodes are 3D positions and the edges represent the topology of the scene), given as an input of our path tracing. We then compute a set of points called \myem{importance points}. These points will be used to sample $\Omega_x$ in the path tracing algorithm. For each node of the skeleton $n$, one importance point $imp_n$ is computed.

Let $L$ be a light source of the scene ($L \in S_L$) and $n_L$ the nearest node that is visible by $L$. We first compute a tree of shortest paths along the skeleton with $n_L$ as root. We use the Dijkstra algorithm with a distance based on visibility from $n_L$: We put $d(n, m) = 1$ if $m$ is visible from $n_L$ and $d(n, m) = 10$ if not. It results that the paths that are enlighted by $L$ will have a shorter distance and will guide us to the light faster than the dark ones.

@@

\subsection{Results and discussion}

We present some results of our algorithm applied to four scenes. The first row shows our result and the second row shows a standard path tracing with the same input parameters. On each picture a MSE (mean square error) value with a reference image is shown.

@@

We presented an application of our skeletonization algorithm for global illumination. Our strategy works well, it reduces noise by taking into account the distribution of energy in the scene. One of the problems is that we take into account only one importance direction for sampling, totally ignoring the BRDF and the cosine factor. A solution called Multiple Importance Sampling will allow us to combine different strategies into one.
